%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tauseef}{Shaikh}{ 
\href{mailto:iamtausif28@gmail.com}{iamtauseef28@gmail.com} | +91 - 8830747885 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Maulana Azad College}
\descript{BCS}
\location{July 2017 | India}
\sectionsep

\subsection{P.M. Paithan}
\descript{12th }
\location{July 2009 | India}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/tasfshaikh}{\bf tasfshaikh} \\
LinkedIn://  \href{https://www.linkedin.com/in/tasfshaikh}{\bf tasfshaikh}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{AWS Cloud Computing}
EC2 \textbullet{}   VPC \textbullet{} S3 \textbullet{} Route53 \\
IAM \textbullet{} ELB \textbullet{} SQS \\ SNS \textbullet{} EBS \textbullet{} Cloud Watch \textbullet{} Cloud Front \textbullet{} Cloud Formation \textbullet{} Maven \textbullet{} Tomcat \textbullet{} jenkins \textbullet{} Ansible \textbullet{} Terraform\\ 
\sectionsep
% \location{Over 1000 lines:}
%  C++ \textbullet{} C Sharp \\
%  \sectionsep
\location{Familiar:}
Docker \textbullet{} Kubernetes
\sectionsep

\subsection{Other}
Git \textbullet{}   AWS \textbullet{} Vs Studio \textbullet{} Windows Admin \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\location{Total Experience - 6+ Years }
\sectionsep
\runsubsection{Bromine Infotech IT Services}
\descript{| Devops Engineer }
\location{Novermber 2021 - Present | Banglore, India} 
\vspace{\topsep}
\begin{tightemize}
\item Collaborated with development teams to ensure seamless integration and delivery of code to production environments. 
\item Implemented and maintained continuous integration and delivery (CI/CD) pipelines using tools such as Jenkins, CircleCi.
\item Managed GitHub repositories and permissions, including branching 
and tagging.
\end{tightemize}
\sectionsep


\runsubsection{Bromine Infotech IT Services}
\descript{| AWS Cloud Engineer}
\location{December 2019 – April 2021 | Aurangabad, India}
\location{(Internship)}
\begin{tightemize}
\item Worked with Cloud Engineer team and understand how to Manage AWS infrastructure.
\item Manage VPC, Subnets Make connection between different Zone block 
suspicious IP via ACL
\item Implemented security best practices for the infrastructure, including encryption and access control, using tools such as AWS KMS and IAM.


\sectionsep
\runsubsection{Dhoot Group Automobile}
\descript{| System Administrator}
\location{March 2017 - August 2019 | Aurangabad, India}
\begin{tightemize}
\item Delivered IT Support 20+ users for a leading Automobile Dealership which included performing database administrator and monitoring system.
\item Perform installations, upgrade, and troubleshooting for users and devices including laptops, desktops, printers, and smartphones devices performance.
\item on-call support to users for OS, MS-Outlook or Application.
\item Mounting NTFS partitions, cd/dvd and usb
\end{tightemize}

\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Web Application Deployment Using Git, Jenkins, and Ansible}
\descript{| Freelance Project a small web development company, needed a way to deploy their web application to multiple environments with ease. The company was manually deploying the application, which was time-consuming and prone to errors. The objective of this project was to automate the deployment process using Git, Jenkins, and Ansible.}
\location{Aug 2022 – Aug 2022}
\sectionsep


\runsubsection{On-Premises to Cloud Migration Project for Dhoot Group}
    \descript{| Dhoot Group, a Automobile Organizations with offices in multiple locations, had been running their applications and databases on their on-premises data centers for many years. The company was facing challenges with performance, and they wanted to leverage the benefits of the cloud, such as cost savings. The cloud infrastructure was optimized for cost savings, resulting in a 30 Percent reduction in infrastructure costs.}
\location{April 2020 – May 2020}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
